\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage[comma,sort&compress]{natbib}
\usepackage{marvosym}
\usepackage{rotating}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{enumitem}
\usepackage{textcomp} %needed for /texttildelow command
%\usepackage{picins,graphicx}
\usepackage{txfonts}
\usepackage[english]{babel}
\geometry{letterpaper, margin=0.75 in}
\renewcommand{\rmdefault}{ptm} % Arial
\renewcommand{\sfdefault}{phv} % Arial
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
\begin{document}
\sloppy \rmfamily
\begin{center}\textbf{NSFA Faculty Position Request\\Date of Submission:~}July 15, 2021\end{center}

\noindent\textbf{Unit:~}SFA\hfill\textbf{Title:~}Dietetic Internship Program Director \hfill \textbf{Start Date:~}Sep 1, 2021\\~\\
\textbf{How does this position address needs in academic programming (i.e., courses taught)?}\\~\\
\small\sffamily The School of Food and Agriculture is home to the nationally accredited Dietetic Internship Program which supplies Registered Dietitian Nutritionists (RDN) to the state and nation. This is an essential service in meeting Maine's workforce needs in health care. The Accreditation Council for Education in Nutrition and Dietetics (ACEND) is the accrediting agency for the Academy of Nutrition and Dietetics, and confers eligibility on our students to sit for the National Registration Examination. The Dietetic Internship Program is a two-year program, with both master’s and doctoral programs available. Our graduates have a high passage rate for the National Registration Exam and are employed readily within the field of dietetics.
\\~\\
A full position description is attached. Key responsibilities for the position include: Plan and teach the Dietetic Internship courses, orientation and Applications I \& II, and Evaluation, and Dietetic Supervised Practice (FSN 650, 651, 652, 681 respectively);  Provide leadership and take major responsibility for FSN 681, Supervised Practice, which includes curriculum planning to adhere to the Competencies outlined by the Accreditation Council for Education in Nutrition and Dietetics (ACEND) for entry-level dietitians; design of evaluation materials; oversight over implementation; coordination of all intern assessments, leading to computing final grades for the 6 credit course; secure the number of supervised practice sites needed for interns accepted into the Program. 
\\~\\
\textbf{\rmfamily How does this position support the research mission of the unit?}\\~\\
The position will not have a research appointment. However, the position supports students who wish to include a research qualification (MS or PhD) to their credentials. 
\newpage
\noindent\textbf{\rmfamily In what ways does this position support College, University, or System initiatives and/or priorities?}
\\~\\
This position directly supports workforce needs of the state in the health professions, provides extensive experiential learning in a clinical practice setting, and can be used to support initiatives in diversity, equity and inclusion through recruitment, training and employment of individuals from under-represented groups.\vfill
\noindent\textbf{\rmfamily Can this position meet any partner accommodation needs (describe)?}\\~\\
The skills are such that this position might be part of an accommodation.\\~\\
\vfill
\noindent\textbf{\rmfamily In what ways does this position support interests of the State, including workforce development?}\\~\\
This position supports the health of Maine's population, Maine's health care-providers, and educates students to enter Maine's health care workforce.\\~\\
\vfill
\newpage\noindent\textbf{\rmfamily What are the anticipated startup needs (items, not just total dollar value)?}\\~\\
None\\~\\
\vfill
\noindent\textbf{\rmfamily Considering all available sources, how do you anticipate meeting the startup needs?}\\~\\
N/A\\~\\
\vfill
\noindent\textbf{\rmfamily What are the anticipated space needs?}\\~\\
An office\\~\\
\vfill
\noindent\textbf{\rmfamily How do you anticipate meeting the space needs?} \\~\\
Using an existing office in SFA space\\~\\
\vfill
\noindent\textbf{\rmfamily Was this position request discussed and approved by the unit faculty?} \hfill ~ \hfill \textbf{\Large{\CrossedBox} \normalsize{Yes}} \hfill \textbf{\Large{\HollowBox} \normalsize{ No}}\\~\\%table373\CrossedBox_tocheckbox
\end{document}
